---
title: "linR_tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linR_tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The 'linR' function performs linear regression analysis and returns a detailed summary of the results. 

## Package installation
If you haven't installed the linR package, ensure it's installed or loaded in your R environment. 
```{r setup}
# install.packages("BIOS625.HW03")
library(BIOS625.HW03)
```

## Function overview

Below is a description of the parameters the function accepts:

- **`formula`**: `response ~ predictor1 + predictor2`.
- **`data`**: The dataset of interest
- **`level`**: The confidence level (default = .95)

## Example

Here is an example of how to use the `linR` function with the `airquality` dataset

- **`formula`**: `Ozone ~ Temp + Wind`
- **`data`**: airquality
- **level`**: 0.95
```{r, echo = TRUE}
# parameters
formula <- Ozone ~ Temp + Wind
data <- airquality
level <- 0.95

# linear regression model
model <- linR(formula, data, level)
```

