---
title: "linR_tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linR_tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
  
## Introduction
  
The 'linR' function performs linear regression analysis and returns a detailed summary of the results. 
  
## Package installation

If you haven't installed the linR package, ensure it's installed or loaded in your R environment. 
```{r setup}
# install.packages("BIOS625.HW03")
library(BIOS625.HW03)
```

## Function overview

Below is a description of the parameters the function accepts:

- **`formula`**: `response ~ predictor1 + predictor2`.
- **`data`**: The dataset of interest
- **`level`**: The confidence level (default = .95)

## Example

Here is an example of how to use the `linR` function with the `airquality` dataset

- **`formula`**: `Ozone ~ Temp + Wind`
- **data**: airquality
- **level`**: 0.95
```{r, echo = TRUE}
# parameters
formula <- Ozone ~ Temp + Wind
data <- na.omit(airquality)
level <- 0.95

# linear regression model using linR
linR_model <- linR(formula, data, level = 0.95)

# linear regression model using lm
lm_model <- lm(formula, data)
lm_model_summary <- summary(lm_model)
```

(1) Estimated coefficients
```{r}
linR_model$coefficients
```

(2) Fitted values
```{r}
linR_model$fitted_values
```

(3) Residuals
```{r}
linR_model$residuals
```

(4) R-squared
```{r}
linR_model$R_squared
```

(5) Adjusted R-squared
```{r}
linR_model$adj_R_squared
```

(6) t-statistics
```{r}
linR_model$t_values
```

(7) p-values
```{r}
linR_model$p_values
```

(8) F-statistic
```{r}
linR_model$F_statistic
```

(9) Confidence Interval
```{r}
linR_CI_result <- linR_model$CI_table

# lower bound
linR_CI_result$'CI.Lower'

# upper bound
linR_CI_result$'CI.Upper'

# table of both lower and upper CI
linR_model$CI_table

```

## Compare with lm()
```{r}
# Coefficients
all.equal(as.numeric(coef(lm_model)), 
          as.numeric(linR_model$coefficients))

# Fitted values
all.equal(as.numeric(fitted.values(lm_model)),
           as.numeric(linR_model$fitted_values))

# Residuals
all.equal(as.numeric(residuals(lm_model)),
          as.numeric(linR_model$residuals))

# R-squared
all.equal((lm_model_summary$r.squared),
          linR_model$R_squared)

# Adjusted R-squared
all.equal((lm_model_summary$adj.r.squared),
          linR_model$adj_R_squared)

# t-statistics
all.equal(as.numeric(lm_model_summary$coefficients[, "t value"]),
          as.numeric(linR_model$t_values))

# p-values for t-tests
all.equal(as.numeric(lm_model_summary$coefficients[, "Pr(>|t|)"]),
          as.numeric(linR_model$p_values))

# F-statistic
all.equal(as.numeric(lm_model_summary$fstatistic[1]),
          linR_model$F_statistic)

```

# Efficiency

The `bench` package is used to measure the runtime and memory usage of functions to assess their efficiency. Here, we compare the performance of the `linR` function wtih the base of R `lm` function 
```{r}
# load the bench package
library(bench)

benchmark_coef <- bench::mark(
  linR_coef = as.numeric(linR(formula, data)$coefficients),
  lm_coef = as.numeric(coef(lm(formula, data))),
  iterations = 100
)

benchmark_coef[, c("expression", "itr/sec")]

```
The benchmark result shows that `linR` is faster than the base `lm` function for calculating coefficients. This suggests that `linR` function is more efficient. 
